Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish Replication Games

### 2016-03-10 doc/introduction.tex
fixed conflicts

The paper is organized as follows. In Section~\ref{sec:game-model}, we introduce CSR games over general undirected networks and review some relevant existing results on this problem. In Section \ref{sec:main-I}, we  characterize the equilibrium points of the system as maximizers of a well-defined function and theoretically justify that randomization can be quite beneficial for maximizing such function under certain cases. Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function. Through numerous simulation results we show that this method can be indeed quite effective. We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.

>>>>

We use random tree search algorithm to locate Nash equilibrium points in CSR game. The random tree search algorithm is an efficient randomized algorithm for searching the state space of games. The random tree algorithm works by sampling the allocation space of the CSR game. The algorithm searches for the optimum allocation, resulting in the Nash equilibrium.
The random tree search is guided by maximizing a cost function associated with each allocation. The random tree grows multiple tree walks from an initial allocation. The random tree branches the simulation walks to bias the walk toward the optimim allocation and avoiding the local minimas.
Recently, stochastic random tree-based search methods have emerged as an alternative to classic optimization algorithms.  The random tree algorithm has been used to optimize analog circuits \cite{adel2015}, robotic motion planning \cite{Lavalle2006}, and deep learning\cite{silver2016}. In comparison to the classic optimization algorithms such as simulated annealing or hill climbing, the random tree search is more efficient and does not get stuck in local minimas \cite{adel15, Lavalle2006}.

The paper is organized as follows. In Section~\ref{sec:game-model}, we introduce CSR games over general undirected networks and review some relevant existing results on this problem. In Section \ref{sec:main-I}, we  characterize the equilibrium points of the system as maximizers of a well-defined function and theoretically justify that randomization can be quite beneficial for maximizing such function under certain cases. Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function. Through numerous simulation results we show that this method can be indeed quite effective on large scale graphs in practical settings. We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.
